Enhancing instance-level constrained clustering through differential evolution

### 2019-06-12 Papers/DILS/paperDILS.tex
Paper DILS completado texto

\journal{Applied Soft Computing}

@@

\begin{abstract}
Clustering has always been a powerful tool in knowledge discovery. Traditionally unsupervised, it received renewed attention when it was shown to produce better results when provided with new types of information, thus leading to a new kind of semi-supervised learning. This new information can be given in form of instance-level must-link and cannot-link constraints, in which this paper focuses on. We propose the first application of Differential Evolution to the constrained clustering problem, which is a generalization of traditional clustering that considers additional information in the form of constraints. We will compare the results obtained by this proposal to those obtained by previous nature-inspired techniques and by some of the state-of-the-art algorithms on 25 datasets with incremental levels of constraint-based information, supporting our conclusions with the aid of Bayesian statistical tests.
\end{abstract}

\begin{keyword}
constrained clustering, instance-level, must-link, cannot-link, genetic algorithm, differential evolution, Bayesian statistical tests.
\end{keyword}

@@

The constrained clustering problem can be formulated in terms of optimization, so that we can apply various optimization techniques to solve it. As mentioned earlier, it is a difficult problem to solve, so nature-inspired techniques are presented as a promising option to find quality approximate solutions. Nature is the best example of adaptive problem solving since it can apply an optimal strategy suited for each natural phenomenon \cite{fausto2019ants}. Nature-inspired algorithms are designed to emulate natural optimization phenomena, such as evolution, collective behavior of animals, physics laws or even human being-related processes. There have been attempts to solve the constrained clustering problem with nature-inspired algorithms, such as the adaptation of the Biased Random-key Genetic Algorithm (BRKGA) presented in \cite{de2017comparison}. Swarm-based methods have also been applied to constrained clustering, such as the one presented in \cite{xu2013improving}.

Differential Evolution (DE) is an evolution-based algorithm that has proven to be excellent in real-domain problem solving \cite{das2011differential}. In this paper we propose the first DE application to find quality solutions for the constrained clustering problem. In particular, we will take as basis for our proposal one of the DE variants which showed excellent behavior in worldwide competitions, known as SHADE \cite{molina2018insight}. We will make use of the Random-key concept from BRKGA, along with proposing a new fitness function, to build the already mentioned DE variant. We will properly compare the results obtained by our new method with previous nature-inspired algorithms, as well as with the constrained clustering state-of-the-art.

Regarding the organization of this paper, Section \ref{sec:background} reviews the existing knowledge concerning constrained clustering and DE. In Section \ref{sec:brkga} the BRKGA algorithm and its adaptation for constrained clustering will be briefly reviewed. Afterward, the SHADE variant of DE algorithm will be presented in Section \ref{sec:SHADE}. In Section \ref{sec:SHADEadapt} the scheme that allow us to apply SHADE to constrained clustering, including the proposal of a new fitness function, will be presented. Sections from \ref{sec:expSetup} to \ref{sec:analisis} present the experimental setup, results and their analysis respectively. Finally, in Section \ref{sec:conclusiones} conclusions are discussed.

\textcolor{red}{Decir que mientras que en los algoritmos memeticos el host es el GA en DILS el host es ILS, conservando todas sus caracteristicas y añadiendo algunas tecnicas de los GA}

@@

In this section we present the background knowledge concerning constrained clustering (Section \ref{sec:BackCC}), its computational complexity (Section \ref{sec:BackFeas}) and a brief description of some of the state-of-the-art methods for constrained clustering (Section \ref{sec:BackSOTA}). We will also present the basis of the DE optimization method (Section \ref{sec:BackDE}).

@@

Constrained clustering has many applications and has been widely studied in the literature. The first adaptation of a classic clustering method for constrained clustering was proposed in \cite{wagstaff2001constrained}. It involved modifying the widely studied K-means algorithm to take into account instance-level constraints: the already known ML and CL. This method was named COP-kmeans, it introduces a modification to the assignation rule of instances to clusters of the K-means algorithm so that an instance can be assigned to a cluster only if the assignment does not violate any constraint.

In \cite{antoine2012cecm} Constrained Evidential c-means (CECM), a variant of the Evidential c-means (ECM \cite{masson2008ecm}) algorithm is proposed, within the fuzzy clustering family of methods. The particularity of this algorithm is that the membership of instances to a cluster is defined by a probabilistic belief function. This method redefines constraints from the point of view of belief functions and includes them in the fitness function.

@@

\textcolor{red}{Poner aqui una descripción del BRKGA?}

@@

\section{The Dual Iterative Local Search Method}

@@

@@

Cabe destacar que el proceso de optimización descrito hasta el momento es aplicable a cualquier problema de minimización, aunque es claro que axiste una adaptación directa de DILS para problemas de maximización. Además el proceso de búsqueda local empleado para obtener el individuo trial debe ser especificado para cada problema, así como cuestiones de representación numérica y las criterios de parada.

@@

\section{DILS optimization scheme for constrained clustering}

@@

For our experiments we will compare the results obtained by BRKGA$_{CC}$ and SHADE$_{CC}$ over 25 datasets and 3 constraints set for each one of them. Most of these datasets can be found at the \href{https://sci2s.ugr.es/keel/category.php?cat=clas}{Keel-dataset repository} \cite{triguero2017keel}, though some of them have been obtained via
\href{https://scikit-learn.org/stable/datasets/index.html}{\texttt{scikit-learn} python package} \cite{scikit-learn}. We also include 3 artificial datasets in our analysis, namely: \textit{Circles}, \textit{Moons} and \textit{Spiral}, which can be found at GitHub. Table \ref{tab:datasets} displays a summary of every dataset.

@@

Table \ref{tab:params} shows a summary of the parameter setup used for DILS$_{CC}$.

@@

The stop criterion is given by the number of evaluations of the fitness function $f$, which at most will be 300000.

To compare with the state-of-the-art methods mentioned in Section \ref{sec:BackSOTA} we will use the parameters setup shown in Table \ref{tab:paramsSOTA} for the implementation that can be found at \href{https://github.com/GermangUgr/TFG/tree/master/Software}{GitHub}. In all cases the value for $k$ is equal to the number of classes displayed in Table \ref{tab:datasets}.

@@

Table \ref{tab:results10} shows the results for the $SC_{10}$ constraint set. We can note that DILS$_{CC}$ represents a consistent improvement over BRKGA$_{CC}$ in both Unsat and Time, while in terms of ARI both methods are similar. This is because the penalty applied to the fitness function of both methods has little presence when operating with a small constraint set, and since they are population-based and heuristic-guided methods, they have similar exploration and exploitation capabilities.

\begin{table}[!h]
	\centering
	\setlength{\tabcolsep}{7pt}
	\renewcommand{\arraystretch}{1.4}
	%\begin{adjustwidth}{-1in}{-1in}
	\resizebox{\textwidth}{!}{
		\begin{tabular}{lccccccc}
			\hline
			Dataset & DILS & BRKGA & COPKM & LCVQE & RDPM & TVClust & CEKM \\
			\hline
			Appendicitis & \textbf{0.611} & 0.022 & - & 0.335 & 0.316 & 0.025 & -0.005 \\
			Breast Cancer & \textbf{0.755} & 0.395 & -0.604 & 0.486 & 0.502 & 0.000 & 0.000 \\
			Bupa & \textbf{0.870} & 0.281 & - & -0.005 & -0.005 & -0.004 & -0.011 \\
			Circles & \textbf{0.798} & 0.166 & - & -0.003 & 0.162 & 0.137 & 0.133 \\
			Ecoli & 0.069 & 0.009 & - & 0.387 & \textbf{0.417} & 0.265 & - \\
			Glass & 0.009 & 0.016 & 0.184 & \textbf{0.268} & 0.197 & 0.211 & - \\
			Haberman & \textbf{0.638} & 0.047 & - & -0.002 & 0.127 & 0.218 & -0.004 \\
			Hayesroth & 0.031 & 0.027 & - & \textbf{0.106} & 0.097 & 0.054 & 0.139 \\
			Heart & \textbf{0.793} & 0.483 & - & 0.027 & 0.036 & 0.423 & -0.003 \\
			Ionosphere & \textbf{0.792} & 0.125 & - & 0.168 & 0.197 & 0.000 & 0.030 \\
			Iris & 0.621 & 0.238 & -0.285 & \textbf{0.730} & 0.607 & 0.244 & 0.684 \\
			Led7Digit & 0.016 & 0.009 & \textbf{0.497} & 0.425 & 0.369 & 0.316 & - \\
			Monk2 & 0.815 & 0.421 & \textbf{0.982} & 0.072 & 0.094 & -0.002 & 0.007 \\
			Moons & \textbf{0.968} & 0.277 & - & 0.241 & 0.319 & 0.785 & 0.092 \\
			Movement Libras & 0.022 & 0.004 & 0.285 & \textbf{0.293} & 0.256 & 0.000 & - \\
			Newthyroid & 0.028 & 0.017 & - & 0.579 & 0.289 & \textbf{0.846} & 0.002 \\
			Saheart & 0.800 & 0.147 & \textbf{0.974} & 0.018 & 0.020 & 0.068 & 0.000 \\
			Sonar & \textbf{0.649} & 0.124 & - & 0.004 & 0.013 & 0.000 & 0.000 \\
			Soybean & 0.304 & 0.496 & 0.503 & 0.545 & \textbf{0.621} & 0.000 & 0.244 \\
			Spectfheart & \textbf{0.896} & 0.334 & - & -0.107 & -0.114 & 0.000 & 0.050 \\
			Spiral & \textbf{0.856} & 0.058 & - & -0.003 & 0.012 & 0.034 & -0.002 \\
			Tae & \textbf{0.031} & 0.018 & - & 0.009 & -0.000 & 0.067 & 0.000 \\
			Vowel & 0.002 & 0.003 & - & 0.063 & -0.003 & \textbf{0.067} & - \\
			Wine & 0.334 & 0.120 & - & 0.360 & \textbf{0.368} & 0.281 & 0.004 \\
			Zoo & 0.151 & 0.105 & \textbf{0.715} & 0.666 & 0.412 & 0.335 & - \\
			\hline
			Mean & \textbf{0.474} & 0.158 & -0.510 & 0.226 & 0.212 & 0.175 & -0.186 \\
			\hline

@@

	\caption{Experimental results obtained for $CS_{10}$ comparing DILS$_{CC}$ and the state-of-the-art.}
	\label{tab:results10}
\end{table}

\begin{table}[!h]
	\centering
	\setlength{\tabcolsep}{7pt}
	\renewcommand{\arraystretch}{1.4}
	%\begin{adjustwidth}{-1in}{-1in}
	\resizebox{\textwidth}{!}{
		\begin{tabular}{lccccccc}
			\hline
			Dataset & DILS & BRKGA & COPKM & LCVQE & RDPM & TVClust & CEKM \\
			\hline
			Appendicitis & \textbf{0.957} & 0.296 & - & 0.305 & 0.284 & 0.025 & -0.006 \\
			Breast Cancer & 0.788 & 0.772 & \textbf{1.000} & 0.486 & 0.502 & 0.000 & 0.037 \\
			Bupa & 0.984 & 0.840 & \textbf{1.000} & -0.005 & -0.007 & -0.007 & 0.001 \\
			Circles & \textbf{1.000} & 0.828 & \textbf{1.000} & -0.003 & 0.375 & 0.973 & 0.105 \\
			Ecoli & 0.134 & 0.015 & - & 0.387 & 0.372 & \textbf{0.719} & - \\
			Glass & 0.057 & 0.017 & - & \textbf{0.280} & 0.253 & 0.229 & - \\
			Haberman & \textbf{1.000} & 0.866 & \textbf{1.000} & -0.002 & 0.075 & 0.219 & -0.050 \\
			Hayesroth & \textbf{0.386} & 0.107 & - & 0.106 & 0.107 & 0.150 & 0.135 \\
			Heart & \textbf{1.000} & 0.692 & \textbf{1.000} & 0.025 & 0.033 & 0.442 & 0.000 \\
			Ionosphere & 0.970 & 0.803 & \textbf{1.000} & 0.178 & 0.212 & 0.000 & 0.057 \\
			Iris & \textbf{0.850} & 0.412 & - & 0.730 & 0.547 & 0.421 & 0.684 \\
			Led7Digit & 0.020 & 0.004 & - & 0.425 & \textbf{0.490} & 0.324 & - \\
			Monk2 & 0.902 & 0.751 & \textbf{1.000} & 0.072 & 0.170 & -0.002 & 0.007 \\
			Moons & \textbf{1.000} & 0.958 & \textbf{1.000} & 0.241 & 0.436 & 0.987 & 0.095 \\
			Movement Libras & 0.025 & 0.006 & -0.742 & \textbf{0.293} & 0.255 & 0.000 & - \\
			Newthyroid & 0.440 & 0.320 & - & 0.568 & 0.356 & \textbf{0.923} & 0.052 \\
			Saheart & 0.862 & 0.749 & \textbf{1.000} & 0.020 & 0.037 & 0.221 & 0.000 \\
			Sonar & \textbf{0.981} & 0.800 & - & 0.004 & 0.019 & 0.000 & 0.000 \\
			Soybean & 0.469 & 0.428 & 0.584 & 0.545 & \textbf{0.605} & 0.000 & 0.000 \\
			Spectfheart & \textbf{1.000} & 0.924 & 0.983 & -0.107 & -0.117 & 0.000 & -0.070 \\
			Spiral & \textbf{1.000} & 0.847 & - & -0.003 & 0.014 & 0.006 & 0.051 \\
			Tae & \textbf{0.299} & 0.119 & - & 0.008 & -0.004 & 0.062 & 0.000 \\
			Vowel & 0.003 & 0.002 & - & 0.063 & -0.003 & \textbf{0.073} & - \\
			Wine & \textbf{0.725} & 0.528 & - & 0.360 & 0.367 & 0.348 & -0.001 \\
			Zoo & 0.185 & 0.157 & 0.435 & \textbf{0.642} & 0.450 & 0.353 & - \\
			\hline
			Mean & \textbf{0.641} & 0.490 & -0.070 & 0.225 & 0.233 & 0.258 & -0.196 \\
			\hline

@@

		\caption{Experimental results obtained for $CS_{15}$ comparing DILS$_{CC}$ and the state-of-the-art.}
		\label{tab:results15}
	\end{table}

\begin{table}[!h]
	\centering
	\setlength{\tabcolsep}{7pt}
	\renewcommand{\arraystretch}{1.4}
	%\begin{adjustwidth}{-1in}{-1in}
	\resizebox{\textwidth}{!}{
		\begin{tabular}{lccccccc}
			\hline
			Dataset & DILS & BRKGA & COPKM & LCVQE & RDPM & TVClust & CEKM \\
			\hline
			Appendicitis & \textbf{1.000} & \textbf{1.000} & - & 0.305 & 0.331 & 0.012 & -0.006 \\
			Breast Cancer & 0.807 & 0.807 & \textbf{1.000} & 0.486 & 0.502 & 0.000 & 0.000 \\
			Bupa & 0.991 & 0.936 & \textbf{1.000} & -0.005 & -0.007 & -0.006 & 0.000 \\
			Circles & \textbf{1.000} & 0.935 & \textbf{1.000} & -0.003 & 0.629 & 1.000 & 0.138 \\
			Ecoli & 0.201 & 0.028 & - & 0.387 & 0.459 & \textbf{0.763} & - \\
			Glass & \textbf{0.322} & 0.038 & - & 0.271 & 0.287 & 0.218 & - \\
			Haberman & \textbf{1.000} & 0.943 & \textbf{1.000} & -0.002 & 0.106 & 0.737 & 0.000 \\
			Hayesroth & \textbf{0.812} & 0.548 & - & 0.106 & 0.107 & 0.208 & 0.056 \\
			Heart & \textbf{1.000} & 0.942 & \textbf{1.000} & 0.025 & 0.033 & 1.000 & 0.000 \\
			Ionosphere & 0.982 & 0.902 & \textbf{1.000} & 0.173 & 0.309 & 0.000 & 0.115 \\
			Iris & \textbf{0.968} & 0.691 & - & 0.708 & 0.540 & 0.585 & 0.684 \\
			Led7Digit & 0.017 & 0.007 & - & 0.425 & \textbf{0.571} & 0.327 & - \\
			Monk2 & 0.904 & 0.855 & \textbf{1.000} & 0.072 & 0.253 & -0.002 & 0.160 \\
			Moons & \textbf{1.000} & 0.937 & \textbf{1.000} & 0.241 & 0.831 & 1.000 & 0.180 \\
			Movement Libras & 0.018 & 0.006 & - & \textbf{0.293} & \textbf{0.293} & 0.000 & - \\
			Newthyroid & 0.842 & 0.848 & - & 0.568 & 0.393 & \textbf{0.933} & 0.004 \\
			Saheart & 0.881 & 0.881 & \textbf{1.000} & 0.018 & 0.026 & \textbf{1.000} & -0.006 \\
			Sonar & \textbf{1.000} & 0.992 & \textbf{1.000} & 0.004 & 0.127 & 0.000 & 0.003 \\
			Soybean & 0.564 & 0.416 & -0.218 & 0.545 & \textbf{0.631} & 0.000 & -0.016 \\
			Spectfheart & \textbf{1.000} & 0.953 & \textbf{1.000} & -0.107 & -0.112 & 0.000 & -0.054 \\
			Spiral & \textbf{1.000} & 0.921 & \textbf{1.000} & -0.003 & 0.011 & 0.006 & 0.045 \\
			Tae & \textbf{0.892} & 0.351 & - & 0.008 & 0.000 & 0.035 & 0.000 \\
			Vowel & 0.003 & 0.002 & - & 0.063 & -0.003 & \textbf{0.071} & - \\
			Wine & 0.916 & \textbf{0.937} & - & 0.360 & 0.363 & 0.380 & 0.015 \\
			Zoo & 0.203 & 0.176 & \textbf{0.821} & 0.642 & 0.439 & 0.335 & - \\
			\hline
			Mean & \textbf{0.733} & 0.642 & 0.064 & 0.223 & 0.285 & 0.344 & -0.187 \\
			\hline

@@

		\caption{Experimental results obtained for $CS_{20}$ comparing DILS$_{CC}$ and the state-of-the-art.}
		\label{tab:results20}
	\end{table}

>>>>

\journal{Computers and Operations Research}

@@

\begin{abstract}
Clustering has always been a powerful tool in knowledge discovery. Traditionally unsupervised, it received renewed attention when it was shown to produce better results when provided with new types of information, thus leading to a new kind of semi-supervised learning. This new information can be given in form of instance-level must-link and cannot-link constraints, in which this paper focuses on. We propose a new heuristic algorithm, the Dual Iterative Local Search, and prrove its capability to provide quiality results for the constrained clustering problem. We will compare the results obtained by this proposal to those obtained by some of the state-of-the-art algorithms on 25 datasets with incremental levels of constraint-based information, supporting our conclusions with the aid of Bayesian statistical tests.
\end{abstract}

\begin{keyword}
constrained clustering, instance-level, must-link, cannot-link, dual iterative local search.
\end{keyword}

@@

The constrained clustering problem can be formulated in terms of optimization, so that we can apply various optimization techniques to solve it. As mentioned earlier, it is a difficult problem to solve, so heuristic techniques are presented as a promising option to find quality approximate solutions. Heuristic algorithms are designed to explore the solution space associated with a problem guided by a fitness (heuristic) function \textcolor{red}{CITA}. In this type of approaches the key is to find a good exploration-exploitation tradeoff. This is the reason why the classic Local Search (LS) algorithm derived in the Iterative Local Search (ILS) algorithm, which introduces periodics perturbations in the exploration of the solutions space to avoid local optima \textcolor{red}{CITA}. Even in ILS the exloitation-exploration tradeoff is unbalanced towards exploitationm, lacking from exploration.

In this paper we propose the Dual Iterative Local Search (DILS) algorithm, which aims to address the exploration lacking problem by using techniques typical of nature-inspired algorithms such as genetic algorithms \textcolor{red}{CITA}. To put it simple, we use ILS as the host algorithm and introduce genetic algorithm operators and an adaptative reinitialization method to encourage exploration of the solution space. This is contrary to the well-known tendency to introduce exploitation techniques in over-explorative algorithm \textcolor{red}{CITA}. In them the host algorithm is usually evolutionary and methods such as LS or simulated annealing \textcolor{red}{CITA} are used to find a better balance between exploration and exploitation \textcolor{red}{CITA}. An example of this are memetic algorithms \textcolor{red}{CITA}.

Regarding the organization of this paper, Section \ref{sec:background} reviews the existing knowledge concerning constrained clustering and the state-of-the-art. In Sections \ref{sec:DILS} and \ref{sec:DILS_CC} the DILS algorithm and its constrained clustering formulation will be reviewed. Sections from \ref{sec:expSetup} to \ref{sec:analisis} present the experimental setup, results and their analysis respectively. Finally, in Section \ref{sec:conclusiones} conclusions are discussed.

@@

In this section we present the background knowledge concerning constrained clustering (Section \ref{sec:BackCC}), its computational complexity (Section \ref{sec:BackFeas}) and a brief description of some of the state-of-the-art methods for constrained clustering (Section \ref{sec:BackSOTA}).

@@

The first adaptation of a classic clustering method for constrained clustering was proposed in \cite{wagstaff2001constrained}. It involved modifying the widely studied K-means algorithm to take into account instance-level constraints: the already known ML and CL. This method was named COP-kmeans, it introduces a modification to the assignation rule of instances to clusters of the K-means algorithm so that an instance can be assigned to a cluster only if the assignment does not violate any constraint.

In \cite{antoine2012cecm} Constrained Evidential c-means (CECM), a variant of the Evidential c-means (ECM \cite{masson2008ecm}) algorithm is proposed, within the fuzzy clustering family of methods. The particularity of this algorithm is that the membership of instances to a cluster is defined by a probabilistic belief function. This method redefines constraints from the point of view of belief functions and includes them in the cost function.

@@

An adaptation of the Biased Random-Key Genetic Algorithm (BRKGA) \cite{gonccalves2011biased}---a variant of the Random-Key genetic algorithm \cite{bean1994genetic}---for the constrained clustering problem is proposed in \cite{de2017comparison}. It uses a genetic algorithm, combined with a local search procedure and guided by a penalty-style fitness function, to obtain a partition of the input dataset. It constitutes one of the few approaches to constrained clustering from the point of view of the evolutionary computing.

@@

\section{The Dual Iterative Local Search Method} \label{sec:DILS}

@@

\textcolor{red}{Poner los inputs}

@@

@@

\section{DILS optimization scheme for constrained clustering} \label{sec:DILS_CC}

@@

For our experiments we will compare the results obtained by DILS$_{CC}$ and state-of-the-art methods over 25 datasets and 3 constraint sets for each one of them. Most of these datasets can be found at the \href{https://sci2s.ugr.es/keel/category.php?cat=clas}{Keel-dataset repository} \cite{triguero2017keel}, though some of them have been obtained via
\href{https://scikit-learn.org/stable/datasets/index.html}{\texttt{scikit-learn} python package} \cite{scikit-learn}. We also include 3 artificial datasets in our analysis, namely: \textit{Circles}, \textit{Moons} and \textit{Spiral}, which can be found at \href{https://github.com/GermangUgr/DILS_CC}{GitHub}. Table \ref{tab:datasets} displays a summary of every dataset.

@@

Table \ref{tab:params} shows a summary of the parameter setup used for the DILS$_{CC}$.

@@

The stop criterion is given by the number of evaluations of the fitness function $f$, which at most will be 300000. The implementation for DILS$_{CC}$ can be found at \href{https://github.com/GermangUgr/DILS_CC}{GitHub}.

To compare with the state-of-the-art methods mentioned in Section \ref{sec:BackSOTA} we will use the parameters setup shown in Table \ref{tab:paramsSOTA} for the implementation that can be found at \href{https://github.com/GermangUgr/TFG/tree/master/Software}{GitHub}. The implementation for the BRKGA algorith can be found in the same link as DILS$_{CC}$. In all cases the value for $k$ is equal to the number of classes displayed in Table \ref{tab:datasets}.

\textcolor{red}{Meter todos los algoritmos en el mismo repo?}

@@

\begin{table}[!h]
	\centering
	\setlength{\tabcolsep}{7pt}
	\renewcommand{\arraystretch}{1.4}
	%\begin{adjustwidth}{-1in}{-1in}
	\resizebox{\textwidth}{!}{
		\begin{tabular}{lccccccc}
			\hline
			Dataset & DILS$_{CC}$ & BRKGA & COPKM & LCVQE & RDPM & TVClust & CEKM \\
			\hline
			Appendicitis & \textbf{0.611} & 0.022 & - & 0.335 & 0.316 & 0.025 & -0.005 \\
			Breast Cancer & \textbf{0.755} & 0.395 & -0.604 & 0.486 & 0.502 & 0.000 & 0.000 \\
			Bupa & \textbf{0.870} & 0.281 & - & -0.005 & -0.005 & -0.004 & -0.011 \\
			Circles & \textbf{0.798} & 0.166 & - & -0.003 & 0.162 & 0.137 & 0.133 \\
			Ecoli & 0.069 & 0.009 & - & 0.387 & \textbf{0.417} & 0.265 & - \\
			Glass & 0.009 & 0.016 & 0.184 & \textbf{0.268} & 0.197 & 0.211 & - \\
			Haberman & \textbf{0.638} & 0.047 & - & -0.002 & 0.127 & 0.218 & -0.004 \\
			Hayesroth & 0.031 & 0.027 & - & \textbf{0.106} & 0.097 & 0.054 & 0.139 \\
			Heart & \textbf{0.793} & 0.483 & - & 0.027 & 0.036 & 0.423 & -0.003 \\
			Ionosphere & \textbf{0.792} & 0.125 & - & 0.168 & 0.197 & 0.000 & 0.030 \\
			Iris & 0.621 & 0.238 & -0.285 & \textbf{0.730} & 0.607 & 0.244 & 0.684 \\
			Led7Digit & 0.016 & 0.009 & \textbf{0.497} & 0.425 & 0.369 & 0.316 & - \\
			Monk2 & 0.815 & 0.421 & \textbf{0.982} & 0.072 & 0.094 & -0.002 & 0.007 \\
			Moons & \textbf{0.968} & 0.277 & - & 0.241 & 0.319 & 0.785 & 0.092 \\
			Movement Libras & 0.022 & 0.004 & 0.285 & \textbf{0.293} & 0.256 & 0.000 & - \\
			Newthyroid & 0.028 & 0.017 & - & 0.579 & 0.289 & \textbf{0.846} & 0.002 \\
			Saheart & 0.800 & 0.147 & \textbf{0.974} & 0.018 & 0.020 & 0.068 & 0.000 \\
			Sonar & \textbf{0.649} & 0.124 & - & 0.004 & 0.013 & 0.000 & 0.000 \\
			Soybean & 0.304 & 0.496 & 0.503 & 0.545 & \textbf{0.621} & 0.000 & 0.244 \\
			Spectfheart & \textbf{0.896} & 0.334 & - & -0.107 & -0.114 & 0.000 & 0.050 \\
			Spiral & \textbf{0.856} & 0.058 & - & -0.003 & 0.012 & 0.034 & -0.002 \\
			Tae & \textbf{0.031} & 0.018 & - & 0.009 & -0.000 & 0.067 & 0.000 \\
			Vowel & 0.002 & 0.003 & - & 0.063 & -0.003 & \textbf{0.067} & - \\
			Wine & 0.334 & 0.120 & - & 0.360 & \textbf{0.368} & 0.281 & 0.004 \\
			Zoo & 0.151 & 0.105 & \textbf{0.715} & 0.666 & 0.412 & 0.335 & - \\
			\hline
			Mean & \textbf{0.474} & 0.158 & -0.510 & 0.226 & 0.212 & 0.175 & -0.186 \\
			\hline

@@

	\caption{Experimental results obtained for $CS_{10}$ by DILS$_{CC}$ and the state-of-the-art methods.}
	\label{tab:results10}
\end{table}

Table \ref{tab:results10} shows the results for the $SC_{10}$ constraint set. We can note that DILS$_{CC}$ represents a consistent improvement over all other 5 methods, specially in the case of BRKGA. This is due to the fact that the exploitation capacity of DILS$_{CC}$ allows it to take better advantage of the information contained in the constraint set than the rest of the methods.

\begin{table}[!h]
	\centering
	\setlength{\tabcolsep}{7pt}
	\renewcommand{\arraystretch}{1.4}
	%\begin{adjustwidth}{-1in}{-1in}
	\resizebox{\textwidth}{!}{
		\begin{tabular}{lccccccc}
			\hline
			Dataset & DILS$_{CC}$ & BRKGA & COPKM & LCVQE & RDPM & TVClust & CEKM \\
			\hline
			Appendicitis & \textbf{0.957} & 0.296 & - & 0.305 & 0.284 & 0.025 & -0.006 \\
			Breast Cancer & 0.788 & 0.772 & \textbf{1.000} & 0.486 & 0.502 & 0.000 & 0.037 \\
			Bupa & 0.984 & 0.840 & \textbf{1.000} & -0.005 & -0.007 & -0.007 & 0.001 \\
			Circles & \textbf{1.000} & 0.828 & \textbf{1.000} & -0.003 & 0.375 & 0.973 & 0.105 \\
			Ecoli & 0.134 & 0.015 & - & 0.387 & 0.372 & \textbf{0.719} & - \\
			Glass & 0.057 & 0.017 & - & \textbf{0.280} & 0.253 & 0.229 & - \\
			Haberman & \textbf{1.000} & 0.866 & \textbf{1.000} & -0.002 & 0.075 & 0.219 & -0.050 \\
			Hayesroth & \textbf{0.386} & 0.107 & - & 0.106 & 0.107 & 0.150 & 0.135 \\
			Heart & \textbf{1.000} & 0.692 & \textbf{1.000} & 0.025 & 0.033 & 0.442 & 0.000 \\
			Ionosphere & 0.970 & 0.803 & \textbf{1.000} & 0.178 & 0.212 & 0.000 & 0.057 \\
			Iris & \textbf{0.850} & 0.412 & - & 0.730 & 0.547 & 0.421 & 0.684 \\
			Led7Digit & 0.020 & 0.004 & - & 0.425 & \textbf{0.490} & 0.324 & - \\
			Monk2 & 0.902 & 0.751 & \textbf{1.000} & 0.072 & 0.170 & -0.002 & 0.007 \\
			Moons & \textbf{1.000} & 0.958 & \textbf{1.000} & 0.241 & 0.436 & 0.987 & 0.095 \\
			Movement Libras & 0.025 & 0.006 & -0.742 & \textbf{0.293} & 0.255 & 0.000 & - \\
			Newthyroid & 0.440 & 0.320 & - & 0.568 & 0.356 & \textbf{0.923} & 0.052 \\
			Saheart & 0.862 & 0.749 & \textbf{1.000} & 0.020 & 0.037 & 0.221 & 0.000 \\
			Sonar & \textbf{0.981} & 0.800 & - & 0.004 & 0.019 & 0.000 & 0.000 \\
			Soybean & 0.469 & 0.428 & 0.584 & 0.545 & \textbf{0.605} & 0.000 & 0.000 \\
			Spectfheart & \textbf{1.000} & 0.924 & 0.983 & -0.107 & -0.117 & 0.000 & -0.070 \\
			Spiral & \textbf{1.000} & 0.847 & - & -0.003 & 0.014 & 0.006 & 0.051 \\
			Tae & \textbf{0.299} & 0.119 & - & 0.008 & -0.004 & 0.062 & 0.000 \\
			Vowel & 0.003 & 0.002 & - & 0.063 & -0.003 & \textbf{0.073} & - \\
			Wine & \textbf{0.725} & 0.528 & - & 0.360 & 0.367 & 0.348 & -0.001 \\
			Zoo & 0.185 & 0.157 & 0.435 & \textbf{0.642} & 0.450 & 0.353 & - \\
			\hline
			Mean & \textbf{0.641} & 0.490 & -0.070 & 0.225 & 0.233 & 0.258 & -0.196 \\
			\hline

@@

	\caption{Experimental results obtained for $CS_{15}$ by DILS$_{CC}$ and the state-of-the-art methods.}
	\label{tab:results15}
\end{table}

Results obtained with the $SC_{15}$ constraint set are presented in Table \ref{tab:results15}. We observe how DILS$_{CC}$ and COPKM are able to obtain partitions of the datasets perfectly coincidents with the true partitions. The fact that DILS$_{CC}$ is always able to output a partition of the datasets is worth the advantage over COPKM. It is even the case that COPKM is not able to provide an output partition while DILS finds the optimal partition or very close to the optimal partition for the same datasets.

\begin{table}[!h]
	\centering
	\setlength{\tabcolsep}{7pt}
	\renewcommand{\arraystretch}{1.4}
	%\begin{adjustwidth}{-1in}{-1in}
	\resizebox{\textwidth}{!}{
		\begin{tabular}{lccccccc}
			\hline
			Dataset & DILS$_{CC}$ & BRKGA & COPKM & LCVQE & RDPM & TVClust & CEKM \\
			\hline
			Appendicitis & \textbf{1.000} & \textbf{1.000} & - & 0.305 & 0.331 & 0.012 & -0.006 \\
			Breast Cancer & 0.807 & 0.807 & \textbf{1.000} & 0.486 & 0.502 & 0.000 & 0.000 \\
			Bupa & 0.991 & 0.936 & \textbf{1.000} & -0.005 & -0.007 & -0.006 & 0.000 \\
			Circles & \textbf{1.000} & 0.935 & \textbf{1.000} & -0.003 & 0.629 & 1.000 & 0.138 \\
			Ecoli & 0.201 & 0.028 & - & 0.387 & 0.459 & \textbf{0.763} & - \\
			Glass & \textbf{0.322} & 0.038 & - & 0.271 & 0.287 & 0.218 & - \\
			Haberman & \textbf{1.000} & 0.943 & \textbf{1.000} & -0.002 & 0.106 & 0.737 & 0.000 \\
			Hayesroth & \textbf{0.812} & 0.548 & - & 0.106 & 0.107 & 0.208 & 0.056 \\
			Heart & \textbf{1.000} & 0.942 & \textbf{1.000} & 0.025 & 0.033 & 1.000 & 0.000 \\
			Ionosphere & 0.982 & 0.902 & \textbf{1.000} & 0.173 & 0.309 & 0.000 & 0.115 \\
			Iris & \textbf{0.968} & 0.691 & - & 0.708 & 0.540 & 0.585 & 0.684 \\
			Led7Digit & 0.017 & 0.007 & - & 0.425 & \textbf{0.571} & 0.327 & - \\
			Monk2 & 0.904 & 0.855 & \textbf{1.000} & 0.072 & 0.253 & -0.002 & 0.160 \\
			Moons & \textbf{1.000} & 0.937 & \textbf{1.000} & 0.241 & 0.831 & 1.000 & 0.180 \\
			Movement Libras & 0.018 & 0.006 & - & \textbf{0.293} & \textbf{0.293} & 0.000 & - \\
			Newthyroid & 0.842 & 0.848 & - & 0.568 & 0.393 & \textbf{0.933} & 0.004 \\
			Saheart & 0.881 & 0.881 & \textbf{1.000} & 0.018 & 0.026 & \textbf{1.000} & -0.006 \\
			Sonar & \textbf{1.000} & 0.992 & \textbf{1.000} & 0.004 & 0.127 & 0.000 & 0.003 \\
			Soybean & 0.564 & 0.416 & -0.218 & 0.545 & \textbf{0.631} & 0.000 & -0.016 \\
			Spectfheart & \textbf{1.000} & 0.953 & \textbf{1.000} & -0.107 & -0.112 & 0.000 & -0.054 \\
			Spiral & \textbf{1.000} & 0.921 & \textbf{1.000} & -0.003 & 0.011 & 0.006 & 0.045 \\
			Tae & \textbf{0.892} & 0.351 & - & 0.008 & 0.000 & 0.035 & 0.000 \\
			Vowel & 0.003 & 0.002 & - & 0.063 & -0.003 & \textbf{0.071} & - \\
			Wine & 0.916 & \textbf{0.937} & - & 0.360 & 0.363 & 0.380 & 0.015 \\
			Zoo & 0.203 & 0.176 & \textbf{0.821} & 0.642 & 0.439 & 0.335 & - \\
			\hline
			Mean & \textbf{0.733} & 0.642 & 0.064 & 0.223 & 0.285 & 0.344 & -0.187 \\
			\hline

@@

	\caption{Experimental results obtained for $CS_{20}$ by DILS$_{CC}$ and the state-of-the-art methods.}
	\label{tab:results20}
\end{table}
